### 2013-02-16 doc/icml2013/regression.tex
edit

\paragraph{Restricted strong convexity}

In this section, we lower bound the restricted strong convexity constant
$\kappa(\opX_p)$.

@@

With these lemmas in hand, we now give the proof of \refthm{convergence}.
\begin{proof}
By \reflem{lowRank} along with \reflem{lowRankLower} and \reflem{lowRankUpper} (discussed below),
we can control the Frobenius norm of the parameter estimates:
If $n \ge n_1$, then
\begin{align}
  \|\hat M_p - M_p\|_F = O\left( \sigma^3 L^3 R^6 k^{\frac12} \sigmamin(\Sigma_p)^{-1} \sqrt{\frac{\log^3 (1/\delta)}{n}} \right).
  %\|\hat M_p - M_p\|_F = O\left( \frac{\sigma^3 L^3 R^6 \sqrt{k} \log^3 (1/\delta)}{\sqrt{n} (\sigmamin(\Sigma_p) - d^p R^p \sqrt{\frac{p \log(d) \log(1/\delta)}{n}}} \right).
\end{align}
The Frobenius norm upper bounds the operator norm,
so we can directly apply Theorem 5.1 of \cite{AnandkumarGeHsu2012}.
%Let $T^* = M_3^*(W^*, W^*, W^*)$.
%Need to convert error from $\epsilon$
%hit by $(W^\top)^\dagger$
\end{proof}

>>>>

%\paragraph{Restricted strong convexity}

%Let us first lower bound the restricted strong convexity constant
%$\kappa(\opX_p)$:

@@

These lemmas allow us to control the compound parameter error.
We now apply them in the proof of \refthm{convergence}:
\begin{proof}
By \reflem{lowRank} along with \reflem{lowRankLower} and \reflem{lowRankUpper},
we can control the Frobenius norm of the parameter estimates:
If $n \ge n_1$, then
\begin{align}
  \|\hat M_p - M_p\|_F = O\left( \sigma^3 L^3 R^6 k^{\frac12} \sigmamin(\Sigma_p)^{-1} \sqrt{\frac{\log^3 (1/\delta)}{n}} \right).
  %\|\hat M_p - M_p\|_F = O\left( \frac{\sigma^3 L^3 R^6 \sqrt{k} \log^3 (1/\delta)}{\sqrt{n} (\sigmamin(\Sigma_p) - d^p R^p \sqrt{\frac{p \log(d) \log(1/\delta)}{n}}} \right).
\end{align}
The Frobenius norm upper bounds the operator norm,
so we can directly apply Theorem 5.1 of \citet{AnandkumarGeHsu2012}.
%Let $T^* = M_3^*(W^*, W^*, W^*)$.
%Need to convert error from $\epsilon$
%hit by $(W^\top)^\dagger$
\end{proof}
